Corpus Stats

### 2019-03-29 notebooks/corpus_stats_and_plots.Rmd
small changes, additions, new functions
updated loc counts

count_df <- read_rds("../data/final_loc_counts.RDS")
as.tibble(count_df) %>%
  mutate(names = rownames(count_df)) -> cloc

@@

>>>>

count_df <- read_rds("../data/final_loc_counts.RDS")
# rows might need to be cast to integers
class(count_df$r_counts) <- "integer"
class(count_df$c_counts) <- "integer"

as.tibble(count_df) %>%
  mutate(names = rownames(count_df)) -> cloc

@@

First: let's get some of the counts for the beginning of the paper.
```{r}
tot_r <- sum(df$r_counts)
tot_c <- sum(df$c_counts)
nrow(df)
```
